---
title: "p8105_hw5_yq2279"
author: "Qi Yuchen"
date: "2019/11/3"
output: html_document
---

```{r setup, include=FALSE}
library(tidyverse)

knitr::opts_chunk$set(
	echo = TRUE,
	warning = FALSE,
	fig.width = 8, 
  fig.height = 6,
  out.width = "90%"
)

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d

theme_set(theme_minimal() + theme(legend.position = "bottom"))
```

# Problem 1

```{r}
set.seed(10)

iris_with_missing = iris %>% 
  map_df(~replace(.x, sample(1:150, 20), NA)) %>%
  mutate(Species = as.character(Species))
```

### The function for replacing missing values

```{r}
fill_na = function(x){
  if (is.numeric(x)) {
    x = replace_na(x, mean(x, na.rm = TRUE))
  }
  else if (is.character(x)) {
    x = replace_na(x, "virginica")
  }
  else {
  stop("Not a valid input")
  }
  
  x
}
```

### Apply the function to the columns of iris_with_missing

```{r}
iris_na_filled = map_df(iris_with_missing, fill_na)
```

# Problem 2

### A dataframe containing all file names

```{r}
df_1 = tibble(
  file_name = list.files("data", full.names = TRUE)
)
```

### Read in data

```{r}
df_2 = df_1 %>% 
  mutate(data = map(file_name, read_csv))
```

### Tidy the result

```{r}
df = df_2 %>%
  unnest(data) %>% 
  mutate(
    file_name = str_replace(file_name, "data/", ""),
    file_name = str_replace(file_name, "\\.csv", "")
    ) %>% 
  mutate(subject = file_name) %>% 
  separate(file_name, into = c("arm", "ID"), sep = "_") %>% 
  mutate(arm = as.factor(arm)) %>% 
  select(-ID) %>% 
  pivot_longer(week_1:week_8, names_to = "week", names_prefix = "week_" ,values_to = "observation") 
```

### Make a spaghetti plot

```{r}
df %>% 
  ggplot(aes(x = week, y = observation, group = subject, color = arm)) +
  geom_line() +
  labs(
    title = " Observations on each subject over time"
  )
```

The observations from the experimental group are genarally larger than the control group.

# Problem 3

### beta1 = 0

```{r}
# one example
n = 30
x = rnorm(n)
beta0 = 2
var = 50
sd = sqrt(var)

beta1 = 0

y = beta0 + beta1 * x + rnorm(n, 0, sd)

ls_fit = lm(y ~ x)
result = broom::tidy(ls_fit) %>% 
  filter(term == "x") %>% 
  janitor::clean_names() %>% 
  select(estimate, p_value)

# define the function for simulation
sim_regression = function(n = 30, beta0 = 2, beta1, sd = sqrt(50)) {
  
  sim_data = tibble(
    x = rnorm(n),
    y = beta0 + beta1 * x + rnorm(n, 0, sd)
  )
  
  ls_fit = lm(y ~ x, data = sim_data)
  
  broom::tidy(ls_fit) %>% 
    filter(term == "x") %>% 
    janitor::clean_names() %>% 
    select(estimate, p_value)
}

# generate 10000 datasets
sim_results = 
  rerun(10000, sim_regression(beta1 = 0)) %>% 
  bind_rows()

knitr::kable(sim_results[1:10,])
```

### beta1 = 0:6

```{r}
sim_results = 
  tibble(beta1 = c(0:6)) %>% 
  mutate(
    output_lists = map(.x = beta1, ~rerun(10000, sim_regression(beta1 = .x))),
    est_p_dfs = map(output_lists, bind_rows)) %>% 
  select(-output_lists) %>% 
  unnest(est_p_dfs)

knitr::kable(sim_results[1:10,])
```

### Make a plot showing the proportion of times the null was rejected

```{r}
# a function to decide rejecting the null or not
h_test = function(p){
  if (p < 0.05) {
    return(1) # 1 means rejecting the null
  } else {
    return(0) # 0 means not rejecting
  }
}

sim_results %>% 
  mutate(reject = map_dbl(p_value, h_test)) %>% 
  group_by(beta1) %>% 
  summarise(proportion_reject = mean(reject)) %>% 
  ggplot(aes(x = beta1, y = proportion_reject)) +
  geom_point() + geom_line()
```

Power increases as effect size increases.

### Make a plot showing the average estimate of beta1

```{r}
sim_results %>% 
  group_by(beta1) %>% 
  summarise(ave_est = mean(estimate)) %>% 
  ggplot(aes(x = beta1, y = ave_est)) +
  geom_point() + geom_line()
```

### Only in samples for which the null was rejected

```{r}
sim_results %>% 
  mutate(reject = map_dbl(p_value, h_test)) %>%
  filter(reject == 1) %>% 
  group_by(beta1) %>% 
  summarise(ave_est = mean(estimate)) %>% 
  ggplot(aes(x = beta1, y = ave_est)) +
  geom_point() + geom_line()
```

The sample average of beta1 across tests for which the null is rejected is not approximately equal to the true value of beta1.